Current Sheets in the Solar Wind: JUNO Observations in the Outer Heliosphere

### 2024-05-13 notes.qmd
update figure

### 02/26/2024

@@

{{< embed notebooks/archive/05_sea.ipynb#fig-fit-params >}}
:::

@@

{{< embed notebooks/04_properties.ipynb#fig-jno-8hz-tau-20-der >}}

@@

<!-- ::: {.column-screen layout-nrow="1"}

![Effect of the time resolution on the discontinuity properties](figures/ts_effect_fit_new)

![Effect of the time resolution on the discontinuity properties](figures/ts_effect)

::: -->

>>>>

<!-- 
### 02/26/2024

@@

{{< embed notebooks/archive/05_sea.ipynb#fig-fit-params >}}
::: 
-->

@@

<!-- {{< embed notebooks/04_properties.ipynb#fig-jno-8hz-tau-20-der >}} -->

@@

<!-- 
::: {.column-screen layout-nrow="1"}
![Effect of the time resolution on the discontinuity properties](figures/ts_effect_fit_new)

![Effect of the time resolution on the discontinuity properties](figures/ts_effect)
:::
-->

### 2024-05-13 presentations/rMeeting.qmd
update
update figure

# References

>>>>

## Motivation

Studying the radial evolution of solar wind discontinuities from observations of PSP (0.1 AU – 1 AU) and JUNO (1AU – 5AU) with Earth-orbiting missions (ARTEMIS, Wind) during aligned intervals.

## Methods

![Time resolution effect](../figures/method/time_res_effect.png)

![Tau effect](../figures/method/tau_effect.png)

## References
